A Standardized Effect Size for Evaluating the Strength of Phylogenetic Signal, and Why Lambda is not Appropriate

### 2020-04-28 Manuscript/Manuscript-3.Rmd
vsn 3

\textbf{Figure 4}.  Variation in estimates of phylogenetic signal across input levels of phylogenetic signal. (A) Estimates of Pagel's $\lambda$ for data simulated on phylogenies with 128 taxa ($n=128$), (B) Estimates of $Z_K$ for data simulated on phylogenies with 128 taxa ($n=128$), (C) Variance in the variation of $\lambda_{est}$ across input levels of phylogenetic signal, estimated on phylogenies containing differing numbers of species. (D) Variance in the variation of $Z_K$ across input levels of phylogenetic signal, estimated on phylogenies containing differing numbers of species.

@@

\singlespacing \textbf{Figure 4}.  Variation in estimates of phylogenetic signal across input levels of phylogenetic signal. (A) Estimates of Pagel's $\lambda$ for data simulated on phylogenies with 128 taxa ($n=128$), (B) Estimates of $Z_K$ for data simulated on phylogenies with 128 taxa ($n=128$), (C) Variance in the variation of $\lambda_{est}$ across input levels of phylogenetic signal, estimated on phylogenies containing differing numbers of species. (D) Variance in the variation of $Z_K$ across input levels of phylogenetic signal, estimated on phylogenies containing differing numbers of species.

>>>>

\textbf{Figure 4}. Variation in effect size estimates of phylogenetic signal across input levels of phylogenetic signal. (A) Estimates $Z_\lambda$ for data simulated on phylogenies with 32 taxa ($n=32$), (B) Estimates of $Z_K$ for data simulated on phylogenies with 32 taxa ($n=32$), (C) Coefficients of variation of precision estimates of $Z_\lambda$ and $Z_K$ across input levels of phylogenetic signal, estimated on phylogenies containing differing numbers of species.

\textbf{Figure 5}.  (A) Linear measures for relative body size, and regions of the body used to estimate surface area to volume (SA:V) ratios. (B) Permutation distributions of phylogenetic signal for SA:V and $\frac{BW}{SVL}$, with observed values shown as vertical bars. (C) Effect sizes ($Z_K$) for SA:V and $\frac{BW}{SVL}$, with their 95% confidence intervals (CI not standardized by $\sqrt(n)$).

@@

\singlespacing \textbf{Figure 4}.  Variation in effect size estimates of phylogenetic signal across input levels of phylogenetic signal. (A) Estimates $Z_\lambda$ for data simulated on phylogenies with 32 taxa ($n=32$), (B) Estimates of $Z_K$ for data simulated on phylogenies with 32 taxa ($n=32$), (C) Coefficients of variation of precision estimates of $Z_\lambda$ and $Z_K$ across input levels of phylogenetic signal, estimated on phylogenies containing differing numbers of species.

```{r, echo = FALSE, out.width="95%"}
include_graphics("Fig5.png")

\singlespacing \textbf{Figure 5}.  (A) Linear measures for relative body size, and regions of the body used to estimate surface area to volume (SA:V) ratios. (B) Permutation distributions of phylogenetic signal for SA:V and $\frac{BW}{SVL}$, with observed values shown as vertical bars. (C) Effect sizes ($Z_K$) for SA:V and $\frac{BW}{SVL}$, with their 95% confidence intervals (CI not standardized by $\sqrt(n)$).
